Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2018-03-19 QPQ9/Submit/qpq9_arXiv.tex
Fourth resubmission. Accepted. Made the final version for arXiv

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}.
We find that the mean absorptions exhibit large velocity widths
$\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
the systemic redshifts. The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems.
We find the observed widths are consistent with gas in gravitational
motion and Hubble flow. However, while the observation of large widths alone does not require
galactic-scale outflows, the observed offsets suggest that the gas is on average outflowing from the
galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
is anisotropic {\bf and/or} intermittent.
\end{abstract}

\keywords{glaxies: clusters: intracluster medium -- galaxies: formation -- galaxies: halos --
intergalactic medium -- quasars: absorption lines -- quasars: general}

@@

We test the case of Hubble flows versus galactic-scale outflows in producing the putative
asymmetry.
{\bf
Anistropic emission is degenerate with intermittent emission in their asymmetric
light-echo in the observer's frame. We first consider the scenario where
the quasar's lifetime is infinite, and the observed ansymmetric absorption is only produced by
anisotropic emission.}
We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
reproduce an absorption centroid that is redshifted from the systemic. In QPQ6, we argued that
the observed anisotropic clustering of optically thick systems around quasars demands that a quasar's
radiation field must affect optically thick systems on Mpc scales. Hence in this test, we set the
incidence of absorbers happening within the quasar opening angle to be zero, for absorbers at all
disances from the quasar. In the case without
outflows, even if we set the opening angle to be $180^\circ$, i.e.\ absorption only happens at
positive velocities, the mean absorption centroid would merely reach $\approx+85\,{\rm km\,s^{-1}}$.
Hence, the observed $\delta v\approx+200\,{\rm km\,s^{-1}}$ shift in the mean absorption cannot be
produced by asymmetric distribution in Hubble velocities alone. This suggests the presence of an
outflow component to account for extra asymmetry in line-of-sight velocities.
{\bf In order to produce the observed intrinsic dispersion and centroid of the mean absorption by
\ion{C}{2}, we must add a radial outflow speed of $\approx450\,{\rm km\,s^{-1}}$ to the absorbers
and a unipolar quasar opening angle of $\approx180^\circ$.
Next, we consider another scenario where the quasar is isotropic, and the asymmetric absorption
is only produced by short episodic lifetime. We further make the assumption the luminosity is
constant during a quasar episode. In the quasar's rest frame, the light echo
would be observed as a spherical region with the quasar at the origin. In the observer's frame, due
to finite light travel time, the light-echo would not be spherically symmetric. The
light-echo from the quasar at its luminosity $t$\,yr earlier traces a paraboloid
with the quasar at the focus and the vertex $t/2$\,ly behind it \citep{Adelberger04,VisbalCroft08}.
We find that, to reproduce the observation, the CGM absorbers need to have a radial outflow speed
$\approx420\,{\rm km\,s^{-1}}$ and the quasar must have shined for $\approx0.4\times10^6$\,yr.
For the anisotropy-only scenario, the opening angle deduced is rather large compared to literature
findings, which give $30^\circ\textendash90^\circ$ \citep[e.g.,][]{TrainorSteidel13,Borisova+16}.
For the intermittence-only scenario, if the quasars are on
averaged observed near the middle of the episode, the lifetime deduced is somewhat small compared
to other existing constraints from observations and simulations, which give
$10^6\textendash10^8$\,yr \citep[e.g.,][]{Martini04,Hopkins+05}.
We thus speculate that the asymmetric absorption is the result of a combination of anisotropic
and intermittent emission.
}

{\bf We note that, \cite{Turner+17} conclude that the clustering of low to intermediate ions around
Lyman-break galaxies in velocity space is
most consistent with gas that is inflowing on average. The different conclusion from our analysis
may originate from the higher masses of our systems, the presence of quasar-driven ouflows
\citep[e.g.,][]{Greene+12}, and/or starburst-driven outflows that are correlated with the presence
of quasars \citep[e.g.,][]{Barthel+17}.}

Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$
measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger
scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study
this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ 2018, in preparation). In conclusion, we
observe large and positively skewed velocity fields in absorption, of metal ions
in the CGM of $z\sim2$ massive galaxies hosting quasars.
We argue that, the observation of large velocity fields alone can be accounted for by
gravitational motions and Hubble flows and does not necessitate outflows. However, we argue that the
positive skew suggests the detected gas is in outflow on average, and the quasars {\bf shine
preferentially toward the observer and/or intermittently.}

@@

\begin{thebibliography}{60}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

>>>>

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}.
We find that the mean absorptions exhibit large velocity widths
$\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
the systemic redshifts. The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems.
We find the observed widths are consistent with gas in gravitational
motion and Hubble flow. However, while the observation of large widths alone does not require
galactic-scale outflows, the observed offsets suggest that the gas is on average outflowing from the
galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
is anisotropic and/or intermittent.
\end{abstract}

\keywords{galaxies: clusters: intracluster medium -- galaxies: formation -- galaxies: halos --
intergalactic medium -- quasars: absorption lines -- quasars: general}

@@

We test the case of Hubble flows versus galactic-scale outflows in producing the putative
asymmetry.
Anistropic emission is degenerate with intermittent emission in their asymmetric
light-echo in the observer's frame. We first consider the scenario where
the quasar's lifetime is infinite, and the observed ansymmetric absorption is only produced by
anisotropic emission.
We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
reproduce an absorption centroid that is redshifted from the systemic. In QPQ6, we argued that
the observed anisotropic clustering of optically thick systems around quasars demands that a quasar's
radiation field must affect optically thick systems on Mpc scales. Hence in this test, we set the
incidence of absorbers happening within the quasar opening angle to be zero, for absorbers at all
disances from the quasar. In the case without
outflows, even if we set the opening angle to be $180^\circ$, i.e.\ absorption only happens at
positive velocities, the mean absorption centroid would merely reach $\approx+85\,{\rm km\,s^{-1}}$.
Hence, the observed $\delta v\approx+200\,{\rm km\,s^{-1}}$ shift in the mean absorption cannot be
produced by asymmetric distribution in Hubble velocities alone. This suggests the presence of an
outflow component to account for extra asymmetry in line-of-sight velocities.
In order to produce the observed intrinsic dispersion and centroid of the mean absorption by
\ion{C}{2}, we must add a radial outflow speed of $\approx450\,{\rm km\,s^{-1}}$ to the absorbers
and a unipolar quasar opening angle of $\approx180^\circ$.
Next, we consider another scenario where the quasar is isotropic, and the asymmetric absorption
is only produced by short episodic lifetime. We further make the assumption the luminosity is
constant during a quasar episode. In the quasar's rest frame, the light echo
would be observed as a spherical region with the quasar at the origin. In the observer's frame, due
to finite light travel time, the light-echo would not be spherically symmetric. The
light-echo from the quasar at its luminosity $t$\,yr earlier traces a paraboloid
with the quasar at the focus and the vertex $t/2$\,ly behind it \citep{Adelberger04,VisbalCroft08}.
We find that, to reproduce the observation, the CGM absorbers need to have a radial outflow speed
$\approx420\,{\rm km\,s^{-1}}$ and the quasar must have shined for $\approx0.4\times10^6$\,yr.
For the anisotropy-only scenario, the opening angle deduced is rather large compared to literature
findings, which give $30^\circ\textendash90^\circ$ \citep[e.g.,][]{TrainorSteidel13,Borisova+16}.
For the intermittence-only scenario, if the quasars are on
averaged observed near the middle of the episode, the lifetime deduced is somewhat small compared
to other existing constraints from observations and simulations, which give
$10^6\textendash10^8$\,yr \citep[e.g.,][]{Martini04,Hopkins+05}.
We thus speculate that the asymmetric absorption is the result of a combination of anisotropic
and intermittent emission.

We note that, \cite{Turner+17} conclude that the clustering of low to intermediate ions around
Lyman-break galaxies in velocity space is
most consistent with gas that is inflowing on average. The different conclusion from our analysis
may originate from the higher masses of our systems, the presence of quasar-driven ouflows
\citep[e.g.,][]{Greene+12}, and/or starburst-driven outflows that are correlated with the presence
of quasars \citep[e.g.,][]{Barthel+17}.

Motivated by the asymmetry found in metal ion absorption in the CGM using precise $z_{\rm fg}$
measurements, and the asymmetry found by \cite{KirkmanTytler08} in \ion{H}{1} on larger
scales, we are assembling a sample of quasar pairs with precise $z_{\rm fg}$ measurements to study
this asymmetry in \ion{H}{1} (J.\ F.\ Hennawi et al.\ 2018, in preparation). In conclusion, we
observe large and positively skewed velocity fields in absorption, of metal ions
in the CGM of $z\sim2$ massive galaxies hosting quasars.
We argue that, the observation of large velocity fields alone can be accounted for by
gravitational motions and Hubble flows and does not necessitate outflows. However, we argue that the
positive skew suggests the detected gas is in outflow on average, and the quasars shine
preferentially toward the observer and/or intermittently.

@@

\begin{thebibliography}{61}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
